---
title: "Thesis Analysis for Gladys Faith Quidasol"
author: "Faith Evangelista-Parsons"
date: "3/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(foreign)

library(tidyverse)
library(dplyr)
library(janitor)
library(haven)
library(survey)
library(readxl)
library(lubridate)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)
library(ggthemes)

```

```{r, echo=FALSE, include=FALSE}
# Import gadget data
gadget   <- read_csv("./data/gadget.csv") %>%
  mutate(Vocab_diff = Vocab_post-Vocab_Pre,
         Grammar_diff = Grammar_Post-Grammar_Pre,
         Total_diff = Total_Post-Total_Pre) 

# Import longhand data 
longhand <- read_csv("./data/longhand.csv") %>%
 mutate(Vocab_diff = Vocab_Post-Vocab_Pre,
         Grammar_diff = Grammar_Post-Grammar_Pre,
         Total_diff = Total_Post-Total_Pre) 


norm_g_total  <- shapiro.test(gadget$Total_diff)
norm_g_gram   <-  shapiro.test(gadget$Grammar_diff)
norm_g_vocab  <- shapiro.test(gadget$Vocab_diff)

norm_lh_total <- shapiro.test(longhand$Total_diff)
norm_lh_gram  <- shapiro.test(longhand$Grammar_diff)
norm_lh_vocab <- shapiro.test(longhand$Vocab_diff)


```


## Test of Normality

The Shapiro Wilk's test was used to assess whether the differences between pre-test and post-test scores follow the normal distribution for grammar, vocabulary, and total scores in the longhand, and the gadget-based group. A p-value > 0.05 indicates that the difference was normally distributed. 


### Gadget Based Group

#### <u>Vocabulary</u>

Shapiro-Wilk: `r norm_g_vocab$statistic`

p-value: `r norm_g_vocab$p.value`

*Interpretation*: The difference between pre- and post-test VOCABULARY scores is normally distributed. 

#### <u> Grammar </u>

Shapiro-Wilk: `r norm_g_gram$statistic`

p-value: `r norm_g_gram$p.value`

*Interpretation*: The difference between pre- and post-test GRAMMAR scores is normally distributed. 


#### <u>Total Score</u>

Shapiro-Wilk: `r norm_g_total$statistic`

p-value: `r norm_g_total$p.value`

*Interpretation*: The difference between pre- and post-test TOTAL scores is normally distributed. 


### <u>Longhand Group</u>

#### Vocabulary

Shapiro-Wilk: `r norm_lh_vocab$statistic`

p-value: `r norm_lh_vocab$p.value`

*Interpretation*: The difference between pre- and post-test VOCABULARY scores is normally distributed. 


#### <u>Grammar</u>

Shapiro-Wilk: `r norm_lh_gram$statistic`

p-value: `r norm_lh_gram$p.value`

*Interpretation*: The difference between pre- and post-test GRAMMAR scores is normally distributed. 


#### <u>Total Score</u>

Shapiro-Wilk: `r norm_lh_total$statistic`

p-value: `r norm_lh_total$p.value`

*Interpretation*: The difference between pre- and post-test TOTAL scores is normally distributed. 



```{r, include=FALSE}
# Paired T-test: Gadget group
t_g_vocab <-   t.test(gadget$Vocab_post,   gadget$Vocab_Pre,  paired=TRUE)
t_g_grammar <- t.test(gadget$Grammar_Post, gadget$Grammar_Pre,paired=TRUE)
t_g_total   <- t.test(gadget$Total_Post,   gadget$Total_Pre,  paired=TRUE)


```

## Paired T-Test

Since the differences between pre- and post-test scores all follow the normal distribution, the paired t-test method was used to assess Hypotheses 1 and 2. 

### Is there a significant difference between the level of oral communication skills of learners before and after using <u>**gadget-based**</u> review technique?

#### <u>Grammar</u>

Mean diff. (Post - Pre): `r t_g_grammar$estimate` 

Std. Dev.: `r sd(gadget$Grammar_diff)`

T-statistic: `r t_g_grammar$statistic`

DF: `r t_g_grammar$parameter`

p-value: `r t_g_grammar$p.value`

*Interpretation*: There is no significant difference in grammar scores before and after  using the gadget-based review technique.


#### <u>Vocabulary</u>

Mean diff (Post - Pre): `r t_g_vocab$estimate` 

Std. Dev.: `r sd(gadget$Vocab_diff)`

T-statistic: `r t_g_vocab$statistic`

DF: `r t_g_vocab$parameter`

p-value: `r t_g_vocab$p.value`

*Interpretation*: There is no significant difference in vocabulary scores before and after using the gadget-based review technique.

#### <u>Total</u>

Mean diff (Post - Pre): `r t_g_total$estimate` 

Std. Dev.: `r sd(gadget$Total_diff)`

T-statistic: `r t_g_total$statistic`

DF: `r t_g_total$parameter`

p-value: `r t_g_total$p.value`

*Interpretation*: There is no significant difference in total scores before and after using the gadget-based review technique.



```{r, include=FALSE}
# Paired T-test: longhand group
t_lh_vocab <-   t.test(longhand$Vocab_Post,   longhand$Vocab_Pre,  paired=TRUE)
t_lh_grammar <- t.test(longhand$Grammar_Post, longhand$Grammar_Pre,paired=TRUE)
t_lh_total   <- t.test(longhand$Total_Post,   longhand$Total_Pre,  paired=TRUE)


```


### Is there a significant difference between the level of oral communication skills of learners before and after using <u>**longhand**</u> review technique?

#### <u>Grammar</u>

Mean diff. (Post - Pre): `r t_lh_grammar$estimate` 

Std. Dev.: `r sd(longhand$Grammar_diff)`

T-statistic: `r t_lh_grammar$statistic`

DF: `r t_lh_grammar$parameter`

p-value: `r t_lh_grammar$p.value`

*Interpretation*: There is no significant difference in grammar scores before and after  using the longhand review technique.


#### <u>Vocabulary</u>

Mean diff (Post - Pre): `r t_g_vocab$estimate` 

Std. Dev.: `r sd(gadget$Vocab_diff)`

T-statistic: `r t_g_vocab$statistic`

DF: `r t_g_vocab$parameter`

p-value: `r t_g_vocab$p.value`

*Interpretation*: There is no significant difference in vocabulary scores before and after using the longhand review technique.

#### <u>Total</u>

Mean diff (Post - Pre): `r t_g_total$estimate` 

Std. Dev.: `r sd(gadget$Total_diff)`

T-statistic: `r t_g_total$statistic`

DF: `r t_g_total$parameter`

p-value: `r t_g_total$p.value`

*Interpretation*: There is no significant difference in total scores before and after using the longhand review technique.


### Is there a significant difference between the level of oral communication skills of learners using gadget-based and longhand review technique?

```{r}
group_compare <- data.frame(
  group = rep(c("Gadget", "Longhand"), each=15),
  vocab_diff = c(gadget$Vocab_diff, longhand$Vocab_diff),
  grammar_diff = c(gadget$Grammar_diff, longhand$Grammar_diff),
  total_diff = c(gadget$Total_diff, longhand$Total_diff)
) 

t_grammar_diff <- t.test(group_compare$grammar_diff~group_compare$group)
t_vocab_diff   <- t.test(group_compare$vocab_diff~group_compare$group)
t_total_diff   <- t.test(group_compare$total_diff~group_compare$group)

```
#### <u>Grammar</u>


T-statistic: `r t_grammar_diff$statistic`

DF: `r t_grammar_diff$parameter`

p-value: `r t_grammar_diff$p.value`

*Interpretation*: There is no significant difference in the change in grammar scores between the gadget-based and longhand technique groups.


#### <u>Vocabulary</u>


T-statistic: `r t_vocab_diff$statistic`

DF: `r t_vocab_diff$parameter`

p-value: `r t_vocab_diff$p.value`

*Interpretation*: There is no significant difference in the change in vocabulary scores between the gadget-based and longhand technique groups.

#### <u>Total</u>

 
T-statistic: `r t_total_diff$statistic`

DF: `r t_total_diff$parameter`

p-value: `r t_total_diff$p.value`

*Interpretation*: There is no significant difference in the change in total scores between the gadget-based and longhand technique groups.


